---
title: "R Notebook"
output: html_notebook
---


#### 1. Construct a 5x3 matrix for the value of x.
```{r}
x = matrix(1:15, nrow=5, ncol=3)
print(x)
```

#### 2. Write program to generate
0 0 0 0  
0 0 0 0  
0 0 0 0  
0 0 0 0
```{r}
matrix(0,nrow=4, ncol=4)
```

#### 3. The object x<-1:8. Write a program to generate the following 3x8 matrix using "cbind(),rbind(),rev(),rep()"
1 2 3 4 5 6 7 8  
8 7 6 5 4 3 2 1  
3 3 3 3 3 3 3 3
```{r}
x = 1:8
rbind(unname(x),rev(x),rep(3,8))
```

#### 4. Chose two different(x,y) 4x4 matrix to perform the following arithmetic operations
##### a. x+y
```{r}
x = matrix(3:18, nrow=4, ncol=4);
y = matrix(1:16, nrow=4, ncol=4);

print(x+y)
```

##### b. x-y
```{r}
print(x-y)
```

##### c. x*y
```{r}
print(x*y)
```

##### d. x%*%y
```{r}
print(x%*%y)
```

##### e. Difference between (c) and (d)
- (c) takes each corresponding element from matrix x and y, and multiply those elements together.
- (d) is the inner product of 2 matrices.

##### f. Inverse of y
```{r}
ginv(y)
```

##### g. z <- x/y
```{r}
z = x/y
print(z)
```
  
##### h. Transpose of z
```{r}
print(t(z))
```
  
##### i. Diagonal of transpose matrix
```{r}
transpose = t(z)
diagonal = diag(transpose)
print(diagonal)
```

#### 5. The difference between (i) and (ii)
(i). x<-matrix(x<-1:9,3,3, byrow = TRUE)  (ii). x<-matrix(x<-1:9, 3, 3)  
  
- (i) creates a matrix by filling the value by row first  
- (ii) creates a matrix by filling the value by column first (the default of matrix() function)


#### 6. Which function can we use for inner product and outer product in matrix calculation?  
  
- Function for inner product is %*%
- Function for outer product is %o%


#### 7. Explain the use of all.equal() function in Matrix with a sample program.
It is a utility to compare R objects x and y testing near equality.
```{r}
all.equal(x,y)
```

#### 8. Explain the use of dim() function with a sample program.
dim() is used to get the dimensions of a matrix. It returns 2 integers. The fist one indicates number of rows and the second one indicates number of columns.
```{r}
dim(x)
```

#### 9. Use of $ operator, and square brackets [] in List with example program.
- $ is used to access an element in a list by name.
- [] is used to access an element in a list by index.

```{r}
a_list = list(type="dog", name="john", age=5)
a_list$type
a_list[2]
```

#### 10. Explain ifelse() with example
This is a shorthand function to the traditional if…else statement.
```{r}
num = 2
ifelse(num %% 2==0, "even", "odd")
```

#### 11. Write a program to get the weight and height from the user to calculate the following cases  
a. If your BMI is less than 18.5, it falls within the underweight range.  
b. If your BMI is 18.5 to <25, it falls within the normal.  
c. If your BMI is 25.0 to <30, it falls within the overweight range.  
d. If your BMI is 30.0 or higher, it falls within the obese range.  
```{r}
weight = as.numeric(readline(prompt = "Enter weight (kg): "))
height = as.numeric(readline(prompt = "Enter height (m): "))

bmi = weight/height^2

if(bmi < 18.5) {
  print("Underweight range")
} else if (bmi < 25) {
  print("Normal")
} else if (bmi < 30) {
  print("Overweight range")
} else {
  print("Obese range")
}
```

#### 12. Difference between List and Data frame
- Data Frame stores a collection of data in a tabular structure and needs to have the same length and other restrictions.
- List is a more flexible data structure in R, and it is similar to data frame but has fewer restrictions.  

##### List
```{r}
ppl = c("we", "wo")
age = c(22, 19)
gender = c("M", "F")
list(people = ppl, age, gender)

```

##### Data Frame
```{r}
data.frame(people = ppl, age, gender)
```

#### 13. Difference between repeat and while loop with example program.
- Repeat loop: it will repeat the chunk of code until you explicitly exit the loop (for example: using break) 
- While loop: it will repeat the code while the given condition is still TRUE.
```{r}
print("repeat loop:")
iter = 1
repeat{
  print(iter)
  iter = iter + 1
  if(iter == 10)
    break
}

print("While loop:")
j = 1
while (j<5) {
  print(j)
  j = j+1
}
```




