---
title: "Unit 1 Assignment"
output: html_notebook
---

# 1. Calculate the following:
### a.  $\Sigma$($a^{4}$ + 5 $a^{3}$) with and without loop.

```{r}
a = 5:100

# WITH loop
result = 0
for (each_a in a) {
  result = result + (each_a^4 + 5*(each_a^3))
}
result


# WITHOUT loop
x = sum(a^4 + 5*a^3)
x
```


### b. Calculate $U_{40}$  which is a series, $U_{n}$ = $U_{n-1}$ + $U_{n-2}$ , with $U_{1}$= 1 and $U_{2}$= 2 ?

```{r}
n = 40
U = 1:n
Un = U[n-1] + U[n-2]
Un
```

### c. Write a program to calculate cos x, sin x(Taylor series) , Get the input(x) from the user and n=45.
```{r}
# cos x
# need pracma package to run taylor function
x = as.numeric(readline(prompt="Enter x: "))
taylor(cos, x, n=4)

# sin x
x = as.numeric(readline(prompt="Enter x: "))
taylor(sin, x, n=4)
```

### d. Create a vector of the values of e^x * cos(x) at x = 3, 3.1, 3.2, . . . , 6.
```{r}
x = seq(3, 6, 0.1)
x = exp(x) * cos(x)
x
```

### e. x <- 1:300. How many numbers in x are divisible by 2?
```{r}
x = 1:300
count = 0L
for(each in x) {
  if(each%%2 == 0) {
    count = count + 1
  }
}
count
```

# 2. Solve the following system of linear equations using Gaussian elimination (Ax=y)
### x + 2y + 3z = 9

### 2x - y + 2z = −3

### 3x + 3y + z = 5
```{r}
a = matrix(c(1, 2, 3,
              2, -1, 2,
              3,  3, 1), 3, 3, byrow=TRUE)

b = c(9, -3, 5)

result = gaussianElimination(a, b)
result
```


# 3. Use outer function to create the following matrix
### 0 1 2 3 4

### 1 2 3 4 5

### 2 3 4 5 6

### 3 4 5 6 7

### 4 5 6 7 8
```{r}
row = 0:4
col = 0:4
outer(row, col, "+")
```

# 4. Get the COVID-19 Dataset from the data sources. Number of observations should be more than 100.Then, report the following informations
### a. Data source detail
```{r}
library(readr)
dataSet <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM")
dataSet
```
### b. Explain the Unit & Necessity of each variable 
```{r}
names(dataSet)
```

### c. Find the missing values(rows & columns) and replace them with mean(Tidy Dataset) 
```{r}

dataSet[] <- lapply(dataSet, function(x) { 
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  x
})
dataSet
```


### d. Generate the two new variables(Var1:Mean, Var2: Median from available variable) 
```{r}
# Click on arrow (on the LEFT of the table) to see Mean and Median columns 
dataSet %>% mutate(Mean = mean(cases),Median = median(cases))
```

### e. Rename the two existing variables
```{r}
dataSet %>% rename(A = countriesAndTerritories, B = geoId)
```

### f. Create a plot using following instructions (using 7 layers of Grammar of Graphics)
#### i. Choose x and y axis(aes) 
```{r}
# Take countriesAndTerritories as x and cases as y
data = dataSet %>% count(countriesAndTerritories, wt = cases)
data
countries = data[['countriesAndTerritories']]
cases = data[['n']]
```

#### ii. geom_point() - specify the parameters, size : 5, color: red, alpha: 1/5
```{r}
gp = geom_point(size = 5, alpha = 1/5, color = "red")
gp
plot = ggplot(x = data, mapping = aes(x = countries, y = cases)) + gp
plot
```


#### iii. Use Facet grid, cartesian coordinates & geom_smooth() 
```{r}
# Facet grid
plot + facet_grid(cases)
```

```{r}
#cartesian coordinates
plot + coord_cartesian()
```
```{r}
#geom_smooth()
plot + geom_smooth(method="lm")
```

#### iv. Assign the title to x, y and graph 
```{r}
plot <- plot + ggtitle("Number of cases of Covid19 in various countries")
plot
```

#### Export the graph to your working directory with the title called “covid_19_dataset.png”
```{r}
ggsave(filename = "covid_19_dataset.png", units = "cm", width = 80, height = 25)

```






Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
